---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  max-width: 1200px;
  margin: 0 auto;
  padding: 20px;
  background-color: #f9f9f9;
}

h2 {
  color: #6b4c3b;
  border-bottom: 3px solid #d4a373;
  padding-bottom: 10px;
  margin-top: 30px;
}

h3 {
  color: #8b5a2b;
  margin-top: 25px;
}

.chart-container {
  background-color: white;
  border-radius: 8px;
  padding: 15px;
  margin: 20px 0;
  box-shadow: 0 2px 4px rgba(0,0,0,0.1);
}

.summary-box {
  background-color: #e9ecef;
  border-left: 5px solid #d4a373;
  padding: 12px 20px;
  margin: 20px 0;
  border-radius: 5px;
}

.highlight {
  font-weight: bold;
  color: #9c6e3e;
  font-size: 1.1em;
}

.footer {
  margin-top: 40px;
  padding-top: 15px;
  border-top: 1px solid #ddd;
  font-size: 0.85em;
  color: #666;
  text-align: center;
}
```

# Coffee Cup Sustainability: An Observational Study
This dynamic report analyzes observational data collected on coffee cup usage patterns across different locations on campus and in local cafes. The data was collected over several days in March 2026, documenting coffee drinkers' choices between reusable and disposable cups.

# Data Overview
A total of 40 coffee drinkers were observed across five different categories. The observations captured information about:

Time of day (hour)

Location where coffee was purchased

Whether the cup was reusable or disposable

Drink size

Estimated age range of the consumer

```{r}
library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS9183XEUL-42O9jbMEUHUd1ziOmdEGUy8sOIzajYTquA66ARBq8jTOWDnZqEtSgiY_I1BNJgQBcq0v/pub?output=csv"

logged_data <- read_csv(csv_url)

# Rename using column positions (like your lab)
latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    hour = 2,
    location = 3,
    reusable = 4,
    size = 5,
    age_range = 6
  )

# Summary 1: Reusable cup count
reusable_table <- latest_data %>%
  select(reusable) %>%
  table()

reusable_count <- reusable_table["Yes"]
total_count <- sum(reusable_table)
reusable_percent <- (reusable_count / total_count) * 100

# Summary 2: Average hour
avg_hour <- mean(latest_data$hour, na.rm = TRUE)
```

Summary 1: `r round(reusable_percent, 1)`% of coffee drinkers used reusable cups.

Summary 2: Average coffee time was `r round(avg_hour, 1)` (between 11am-12pm).

# Bar Chart 1: Reusable Cup Usage by Location

```{r}
ggplot(latest_data, aes(x = location, fill = reusable)) +
  geom_bar() +
  labs(title = "Reusable Cup Usage by Location",
       x = "Location",
       y = "Number of Observations",
       fill = "Reusable?")
```

# Bar Chart 2: Coffee Observations by Hour

```{r}
ggplot(latest_data, aes(x = hour)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Coffee Observations by Hour",
       x = "Hour of Day",
       y = "Number of Observations")
```

# Conclusion
Based on r nrow(latest_data) observations:

1. Reusable cup adoption: `r round(reusable_percent, 1)`%

2. Peak coffee hour: `r avg_hour`

*Data collected for STATS 220*